Resilience and Home-Space for WSTS

### 2024-01-11 diapo/presentation.tex
up

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.47\textwidth]{FigA}
	\end{figure}
\end{center}

@@

   \begin{center}
 	\begin{figure}
% 	\hspace{-2.cm}
\includegraphics[width=.47\textwidth]{FigB}
	\end{figure}
\end{center}

@@

$q_1(9) \to q_0(10) \to q_2(0) \to q_1(0)$

@@

  \begin{block}{Definition~\cite{DBLP:journals/lmcs/BlondinFM17}}
A {\em Well-Behaved Transition System} (WBTS) 
is an ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
all antichains of $(S, \leq)$ are finite, and
%the transition relation 
$ \rightarrow$ is (upward) compatible with $\leq$. 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{block}

\begin{block}{Definition~\cite{DBLP:journals/iandc/Finkel90}}
A {\em Well-Structured Transition System} (WSTS) 
is a well-ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ with 
 $ \rightarrow$ is (upward) compatible with $\leq$. 
%the transition relation $ \rightarrow$ is (upward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{block}

@@

@@

>>>>

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.4\textwidth]{FigA}
	\end{figure}
\end{center}

@@

   \begin{center}
 	\begin{figure}
% 	\hspace{-2.cm}
\includegraphics[width=.4\textwidth]{FigB}
	\end{figure}
\end{center}

@@

$q_1(7) \to q_0(8) \to q_0(9) \to q_0(10) \to q_2(0) \to q_1(0)$

$q_1(6) \to q_1(5) \to q_1(4) \to q_1(3) \to q_1(2) \to q_1(1) \to q_1(0)$

@@

  \begin{block}{Definition~\cite{DBLP:journals/lmcs/BlondinFM17}}
A {\em Well-Behaved Transition System} (WBTS) 
is an ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
all antichains of $(S, \leq)$ are finite, and
%the transition relation 
$ \rightarrow$ is upward-compatible with $\leq$. 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{block}

@@

\begin{block}{Definition~\cite{DBLP:journals/iandc/Finkel90}}
A {\em Well-Structured Transition System} (WSTS) 
is a well-ordered WBTS.
% ward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{block}

@@

\nocite{DBLP:conf/gg/Ozkan22}
